AOI TOI - number of fixations, duration of fixation & time to first fixation

### 2024-03-11 01_studies/01_Laborstudie ProVisioNET/R script/demographic data/demographic data script.Rmd
et

# prepare data (selected from questionnaire data)
demo.data <- readxl::read_xlsx("./data/data_empschul_labor_lehrperson.xlsx")

# select relevant columns
demo.data <- demo.data %>% select(LI02_01_1,
                                  LI03_01,
                                  LI04_01,
                                  LI06_05)

>>>>

# prepare data (selected from questionnaire data)
demo.data <- readxl::read_xlsx("./data/demografic_data_empschul_labor_lehrperson.xlsx")

# select relevant columns
demo.data <- demo.data %>% select(LI02_01_1,
                                  LI03_01,
                                  LI04_01,
                                  LI06_05) %>%
  filter(!LI06_05 %in% c(201,
                         242,
                         141,
                         142))

### 2024-03-11 01_studies/01_Laborstudie ProVisioNET/R script/et aoi/et_aoi.Rmd
et

# Load packages and read in data
```{r}
library(needs)
needs(tidyverse,
      psych,
      moments,
      sjPlot,
      DescTools,
      irr,
      readxl, 
      gridExtra,
      janitor,
      RColorBrewer,
      cowplot)

@@

@@

  # scale_x_discrete(labels = c(
  #   paste(
  #     "Novice\n",
  #     glue("<i>M</i>"),
  #     " = ",
  #     c(mean_number_nov, mean_number_exp)
  #   ),
  #   c(
  #     "Expert\n",
  #     ";",
  #     glue("<i>SD</i>"),
  #     " = ",
  #     c(sd_number_nov, sd_number_exp)
  #   ) 
  # )) +
  labs(x ="",
       y = "Number") +
  scale_fill_brewer(palette  = "RdBu") +  
  ggtitle("Number of Fixations on all AOIs") +
  theme_cowplot() +
  theme(legend.position="none",
        axis.text.x = element_text(size = 34),
        axis.text.y = element_text(size = 18),
        axis.title = element_text(size = 34),
        plot.title = element_text(size = 35, 
                                  face = "bold")
        ) -> plot_number_group
plot_number_group

@@

# plotting average duration on AOI Disruptive person
df_aoi_disrup %>% 
  ggplot(mapping = aes(x = Group,
                       y = Number_of_fixations.Disruptive_Person)) +
  geom_boxplot(mapping = aes(fill = Group),
               outlier.shape = NA) +
  geom_point(size = 2,
             alpha = 0.7,
             position = position_jitter(seed = 1,
                                        width = 0.1,
                                        height = 0.1)) +
  # scale_x_discrete(labels = paste0(c("Novice\n","Expert\n"),
  #                                  "M = ", c(mean_dur_nov, mean_dur_exp),
  #                                  "; SD = ", c(sd_dur_nov, sd_dur_exp)
  #                                  )
  #                  ) +
  labs(x ="",
       y = "Number") + 
  scale_fill_brewer(palette  = "RdBu") +  
  ggtitle("Number of Fixations\non AOI `Disruptive Person`") +
  theme_cowplot() +
  theme(legend.position="none",
        axis.text.x = element_text(size = 34),
        axis.text.y = element_text(size = 18),
        axis.title = element_text(size = 34),
        plot.title = element_text(size = 35, 
                                  face = "bold")
  ) -> plot_number_disrup

@@

# plotting average duration on AOI Students
df_aoi_stud %>% 
  ggplot(mapping = aes(x = Group,
                       y = Stud_number_fixation)) +
  geom_boxplot(mapping = aes(fill = Group),
               outlier.shape = NA) +
  geom_point(size = 2,
             alpha = 0.7,
             position = position_jitter(seed = 1,
                                        width = 0.1,
                                        height = 0.1)) +
  # scale_x_discrete(labels = paste0(c("Novice\n","Expert\n"),
  #                                  "M = ", c(mean_dur_nov, mean_dur_exp),
  #                                  "; SD = ", c(sd_dur_nov, sd_dur_exp)
  #                                  )
  #                  ) +
  labs(x ="",
       y = "Number") + 
  scale_fill_brewer(palette  = "RdBu") +  
  ggtitle("Number of Fixations\non AOI `Students`") +
  theme_cowplot() +
  theme(legend.position="none",
        axis.text.x = element_text(size = 34),
        axis.text.y = element_text(size = 18),
        axis.title = element_text(size = 34),
        plot.title = element_text(size = 35, 
                                  face = "bold")
  ) -> plot_number_stud

>>>>

# Load packages and read in data
```{r}
library(needs)
needs(tidyverse,
      psych,
      moments,
      sjPlot,
      DescTools,
      irr,
      readxl, 
      gridExtra,
      janitor,
      RColorBrewer,
      cowplot,
      svglite)

@@

df_aoi %>% 
  filter(TOI == "Lesson") %>% 
  select (Group,
          Participant,
          starts_with("Total_duration_of_fixations"),
          starts_with("Number_of_fixations"),
          !"Total_duration_of_fixations.Disruptive_Person",
          !"Number_of_fixations.Disruptive_Person") %>% 
  rowwise() %>% 
  transmute(Group = Group,
            Participant = Participant,
            Sum_duration_fixation = sum(c_across(starts_with("Total_duration")
                                                    ),
                                           na.rm = TRUE
                                           ),
            Sum_number_fixation = sum(c_across(starts_with("Number_of")
                                                  ),
                                         na.rm = TRUE
                                         )
            ) %>% 
  mutate(Average_duration = round(Sum_duration_fixation/Sum_number_fixation,
                                         digits = 0),
         Group = as_factor(Group)) %>% 
  drop_na() -> df_aoi_sum

@@

  # scale_x_discrete(labels = c(
  #   paste(
  #     "Novice\n",
  #     glue("<i>M</i>"),
  #     " = ",
  #     c(mean_number_nov, mean_number_exp)
  #   ),
  #   c(
  #     "Expert\n",
  #     ";",
  #     glue("<i>SD</i>"),
  #     " = ",
  #     c(sd_number_nov, sd_number_exp)
  #   ) 
  # )) +
  labs(x ="",
       y = "Anzahl Fixationen") +
  scale_fill_brewer(palette  = "RdBu") +  
  scale_x_discrete(labels=c("Novice" = "Unerfahren",
                            "Expert" = "Erfahren")) +
  ggtitle("Anzahl der Fixationen in allen AOIs") +
  theme_cowplot() +
  theme(legend.position="none",
        axis.text.x = element_text(size = 34),
        axis.text.y = element_text(size = 18),
        axis.title = element_text(size = 34),
        plot.title = element_text(size = 35, 
                                  face = "bold")
        ) -> plot_number_group
plot_number_group

@@

# plotting average duration on AOI Disruptive person
df_aoi_disrup %>% 
  ggplot(mapping = aes(x = Group,
                       y = Number_of_fixations.Disruptive_Person)) +
  geom_boxplot(mapping = aes(fill = Group),
               outlier.shape = NA) +
  geom_point(size = 2,
             alpha = 0.7,
             position = position_jitter(seed = 1,
                                        width = 0.1,
                                        height = 0.1)) +
  # scale_x_discrete(labels = paste0(c("Novice\n","Expert\n"),
  #                                  "M = ", c(mean_dur_nov, mean_dur_exp),
  #                                  "; SD = ", c(sd_dur_nov, sd_dur_exp)
  #                                  )
  #                  ) +
  labs(x ="",
       y = "Anzahl Fixationen") + 
  scale_fill_brewer(palette  = "RdBu") +  
  ggtitle("Anzahl Fixationen AOI\n`Störperson`") +
    scale_x_discrete(labels=c("Novice" = "Unerfahren",
                            "Expert" = "Erfahren")) +
  theme_cowplot() +
  theme(legend.position="none",
        axis.text.x = element_text(size = 34),
        axis.text.y = element_text(size = 18),
        axis.title = element_text(size = 34),
        plot.title = element_text(size = 35, 
                                  face = "bold")
  ) -> plot_number_disrup

@@

# plotting average duration on AOI Students
df_aoi_stud %>% 
  ggplot(mapping = aes(x = Group,
                       y = Stud_number_fixation)) +
  geom_boxplot(mapping = aes(fill = Group),
               outlier.shape = NA) +
  geom_point(size = 2,
             alpha = 0.7,
             position = position_jitter(seed = 1,
                                        width = 0.1,
                                        height = 0.1)) +
  # scale_x_discrete(labels = paste0(c("Novice\n","Expert\n"),
  #                                  "M = ", c(mean_dur_nov, mean_dur_exp),
  #                                  "; SD = ", c(sd_dur_nov, sd_dur_exp)
  #                                  )
  #                  ) +
  labs(x ="",
       y = "Anzahl Fixationen") + 
  scale_fill_brewer(palette  = "RdBu") +  
  ggtitle("Anzahl Fixationen AOI\n`Schüler:innen`") +
  theme_cowplot() +
  scale_x_discrete(labels=c("Novice" = "Unerfahren",
                            "Expert" = "Erfahren")) +
  theme(legend.position="none",
        axis.text.x = element_text(size = 34),
        axis.text.y = element_text(size = 18),
        axis.title = element_text(size = 34),
        plot.title = element_text(size = 35, 
                                  face = "bold")
  ) -> plot_number_stud
